---
title: "Simper_Analysis"
author: "MS"
date: "7/4/2022"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#The `simper` function:
- *comm*: community data matrix.
- *group*: factor describing the group structure. Must have at least 2 levels.


#Value:
- *species*: the species names
- *average*: average contribution to overall dissimilarity
- *overall*: the overall between-group dissimilarity
- *sd*: standard deviation of contribution
- *ratio*: average to sd ratio
- *ava, avb*: average abundances per group
- *ord*: an index vector to order vectors by their contribution or order *cusum* back to the original data order
- *cusum*: ordered cumulative contribution
- *p*: permutation p-value. Probability of getting a larger or equal average contribution in random permutation of the group factor

```{r}
#strain 1021
#Create the objects for the simper function:

library(vegan)
library(reshape2)
setwd("/home/workstation/Scrivania/MARTINA/DEGs Analysis")

strain_1021 <- read.csv("Counts1021.csv", sep = ",")

strain_1021_matrix <- acast(strain_1021, strain_1021$id ~ strain_1021$Sample, value.var = "FoldChange")
strain_1021_matrix[is.na(strain_1021_matrix)] = 0

condition <- factor(c("condition_camporegio_vs_blank","condition_lodi_vs_blank","condition_luteolin_vs_blank", "condition_verbena_vs_blank"))
condition_df <- data.frame(condition)

simp_1021 <- vegan::simper(strain_1021_matrix, group = condition_df$condition)
simp_1021_sum <- summary(simp_1021)


#save the object simp_1021_sum to csv file:
write.csv(simp_1021_sum$condition_camporegio_vs_blank_condition_lodi_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/simper_1021_campor_lodi_1.csv", 
          row.names = TRUE)

write.csv(simp_1021_sum$condition_camporegio_vs_blank_condition_luteolin_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/simper_1021_campor_luteo_1.csv", 
          row.names = TRUE)

write.csv(simp_1021_sum$condition_camporegio_vs_blank_condition_verbena_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/simper_1021_campor_verb_1.csv", 
          row.names = TRUE)

write.csv(simp_1021_sum$condition_lodi_vs_blank_condition_luteolin_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/simper_1021_lodi_luteo_1.csv", 
          row.names = TRUE)

write.csv(simp_1021_sum$condition_lodi_vs_blank_condition_verbena_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/simper_1021_lodi_verb_1.csv", 
          row.names = TRUE)

write.csv(simp_1021_sum$condition_luteolin_vs_blank_condition_verbena_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/simper_1021_luteo_verb_1.csv", 
          row.names = TRUE)

```


```{r}
#strain AK83
#create the objects for the simper function

strain_AK83 <- read.csv("AK83_countdata.csv", sep = ",")

strain_AK83_matrix <- acast(strain_AK83, strain_AK83$id ~ strain_AK83$sample, value.var = "FoldChange")
strain_AK83_matrix[is.na(strain_AK83_matrix)] = 0

simp_AK83 <- vegan::simper(strain_AK83_matrix, group = condition_df$condition)
simp_AK83_sum <- summary(simp_AK83)

#save the object simp_AK83_sum to csv file:
write.csv(simp_AK83_sum$condition_camporegio_vs_blank_condition_lodi_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_AK83/simper_AK83_campor_lodi_ord.csv", 
          row.names = TRUE)

write.csv(simp_AK83_sum$condition_camporegio_vs_blank_condition_luteolin_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_AK83/simper_AK83_campor_luteo_ord.csv", 
          row.names = TRUE)

write.csv(simp_AK83_sum$condition_camporegio_vs_blank_condition_verbena_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_AK83/simper_AK83_campor_verb_ord.csv", 
          row.names = TRUE)

write.csv(simp_AK83_sum$condition_lodi_vs_blank_condition_luteolin_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_AK83/simper_AK83_lodi_luteo_ord.csv", 
          row.names = TRUE)

write.csv(simp_AK83_sum$condition_lodi_vs_blank_condition_verbena_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_AK83/simper_AK83_lodi_verb_ord.csv", 
          row.names = TRUE)

write.csv(simp_AK83_sum$condition_luteolin_vs_blank_condition_verbena_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_AK83/simper_AK83_luteo_verb.ord.csv", 
          row.names = TRUE)


```


```{r}
#strain BL225C
#create the objects for the simper function

strain_BL225C <- read.csv("BL225C_countdata.csv", sep = ",")
strain_BL225C_matrix <- acast(strain_BL225C, strain_BL225C$id ~ strain_BL225C$sample, value.var = "FoldChange")
strain_BL225C_matrix[is.na(strain_BL225C_matrix)] = 0

simp_BL225C <- vegan::simper(strain_BL225C_matrix, group = condition_df$condition)
simp_BL225C_sum <- summary(simp_BL225C)

#save the object simp_BL225C_sum to csv file:
write.csv(simp_BL225C_sum$condition_camporegio_vs_blank_condition_lodi_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_BL225C/simper_BL225C_campor_lodi_ord.csv", 
          row.names = TRUE)

write.csv(simp_BL225C_sum$condition_camporegio_vs_blank_condition_luteolin_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_BL225C/simper_BL225C_campor_luteo_ord.csv", 
          row.names = TRUE)

write.csv(simp_BL225C_sum$condition_camporegio_vs_blank_condition_verbena_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_BL225C/simper_BL225C_campor_verb_ord.csv", 
          row.names = TRUE)

write.csv(simp_BL225C_sum$condition_lodi_vs_blank_condition_luteolin_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_BL225C/simper_BL225C_lodi_luteo_ord.csv", 
          row.names = TRUE)

write.csv(simp_BL225C_sum$condition_lodi_vs_blank_condition_verbena_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_BL225C/simper_BL225C_lodi_verb_ord.csv", 
          row.names = TRUE)

write.csv(simp_BL225C_sum$condition_luteolin_vs_blank_condition_verbena_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_BL225C/simper_BL225C_lueto_verb_ord.csv", 
          row.names = TRUE)



```


```{r}
#strain hybrid
#create the objects for the simper function

strain_hybrid <- read.csv("Hybrid_countdata.csv", sep = ",")
strain_hybrid_matrix <- acast(strain_hybrid, strain_hybrid$id ~ strain_hybrid$sample, value.var = "FoldChange")
strain_hybrid_matrix[is.na(strain_hybrid_matrix)] = 0

simp_hybrid <- vegan::simper(strain_hybrid_matrix, group = condition_df$condition)
simp_hybrid_sum <- summary(simp_hybrid)


#save the object simp_hybrid_sum to csv file:
write.csv(simp_hybrid_sum$condition_camporegio_vs_blank_condition_lodi_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_hybrid/simper_hybrid_campor_lodi_ord.csv", 
          row.names = TRUE)

write.csv(simp_hybrid_sum$condition_camporegio_vs_blank_condition_luteolin_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_hybrid/simper_hybrid_campor_luteo_ord.csv", 
          row.names = TRUE)

write.csv(simp_hybrid_sum$condition_camporegio_vs_blank_condition_verbena_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_hybrid/simper_hybrid_campor_verb_ord.csv", 
          row.names = TRUE)

write.csv(simp_hybrid_sum$condition_lodi_vs_blank_condition_luteolin_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_hybrid/simper_hybrid_lodi_luteo_ord.csv", 
          row.names = TRUE)

write.csv(simp_hybrid_sum$condition_lodi_vs_blank_condition_verbena_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_hybrid/simper_hybrid_lodi_verb_ord.csv", 
          row.names = TRUE)

write.csv(simp_hybrid_sum$condition_luteolin_vs_blank_condition_verbena_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_hybrid/simper_hybrid_luteo_verb_ord.csv", 
          row.names = TRUE)


```
