---
title: "Simper_Analysis"
author: "MS"
date: "7/4/2022"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#The `simper` function:
- *comm*: community data matrix.
- *group*: factor describing the group structure. Must have at least 2 levels.


#Value:
- *species*: the species names
- *average*: average contribution to overall dissimilarity
- *overall*: the overall between-group dissimilarity
- *sd*: standard deviation of contribution
- *ratio*: average to sd ratio
- *ava, avb*: average abundances per group
- *ord*: an index vector to order vectors by their contribution or order *cusum* back to the original data order
- *cusum*: ordered cumulative contribution
- *p*: permutation p-value. Probability of getting a larger or equal average contribution in random permutation of the group factor

```{r}
#strain 1021
#Create the objects for the simper function:

library(vegan)

setwd("/home/workstation/Scrivania/MARTINA/DEGs Analysis")

strain_1021 <- read.csv("Counts1021.csv", sep = ",")

strain_1021_matrix <- acast(strain_1021, strain_1021$id ~ strain_1021$Sample, value.var = "FoldChange")

strain_1021_matrix[is.na(strain_1021_matrix)] = 0

condition <- factor(c("condition_camporegio_vs_blank","condition_lodi_vs_blank","condition_luteolin_vs_blank", "condition_verbena_vs_blank"))

condition_df <- data.frame(condition)

simp_1021 <- vegan::simper(strain_1021_matrix, group = condition_df$condition)

simp_1021_sum <- summary(simp_1021)


#save the object simp_1021_sum to csv file:
write.csv(simp_1021_sum$condition_camporegio_vs_blank_condition_lodi_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/simper_1021_campor_lodi_1.csv", 
          row.names = TRUE)

write.csv(simp_1021_sum$condition_camporegio_vs_blank_condition_luteolin_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/simper_1021_campor_luteo_1.csv", 
          row.names = TRUE)

write.csv(simp_1021_sum$condition_camporegio_vs_blank_condition_verbena_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/simper_1021_campor_verb_1.csv", 
          row.names = TRUE)

write.csv(simp_1021_sum$condition_lodi_vs_blank_condition_luteolin_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/simper_1021_lodi_luteo_1.csv", 
          row.names = TRUE)

write.csv(simp_1021_sum$condition_lodi_vs_blank_condition_verbena_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/simper_1021_lodi_verb_1.csv", 
          row.names = TRUE)

write.csv(simp_1021_sum$condition_luteolin_vs_blank_condition_verbena_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/simper_1021_luteo_verb_1.csv", 
          row.names = TRUE)

```


```{r}
#strain AK83
#create the objects for the simper function

library(vegan)
library(reshape2)

setwd("/home/workstation/Scrivania/MARTINA/DEGs Analysis")

strain_AK83 <- read.csv("AK83_countdata.csv", sep = ",")

strain_AK83_matrix <- acast(strain_AK83, strain_AK83$id ~ strain_AK83$sample, value.var = "FoldChange")

strain_AK83_matrix[is.na(strain_AK83_matrix)] = 0

condition_df

simp_AK83 <- vegan::simper(strain_AK83_matrix, group = condition_df$condition)

simp_AK83_sum <- summary(simp_AK83)

#save the object simp_AK83_sum to csv file:
write.csv(simp_AK83_sum$condition_camporegio_vs_blank_condition_lodi_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_AK83/simper_AK83_campor_lodi_ord.csv", 
          row.names = TRUE)

write.csv(simp_AK83_sum$condition_camporegio_vs_blank_condition_luteolin_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_AK83/simper_AK83_campor_luteo_ord.csv", 
          row.names = TRUE)

write.csv(simp_AK83_sum$condition_camporegio_vs_blank_condition_verbena_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_AK83/simper_AK83_campor_verb_ord.csv", 
          row.names = TRUE)

write.csv(simp_AK83_sum$condition_lodi_vs_blank_condition_luteolin_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_AK83/simper_AK83_lodi_luteo_ord.csv", 
          row.names = TRUE)

write.csv(simp_AK83_sum$condition_lodi_vs_blank_condition_verbena_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_AK83/simper_AK83_lodi_verb_ord.csv", 
          row.names = TRUE)

write.csv(simp_AK83_sum$condition_luteolin_vs_blank_condition_verbena_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_AK83/simper_AK83_luteo_verb.ord.csv", 
          row.names = TRUE)


```


```{r}
#strain BL225C
#create the objects for the simper function

library(vegan)
library(reshape2)

setwd("/home/workstation/Scrivania/MARTINA/DEGs Analysis")

strain_BL225C <- read.csv("BL225C_countdata.csv", sep = ",")

strain_BL225C_matrix <- acast(strain_BL225C, strain_BL225C$id ~ strain_BL225C$sample, value.var = "FoldChange")

strain_BL225C_matrix[is.na(strain_BL225C_matrix)] = 0

condition_df

simp_BL225C <- vegan::simper(strain_BL225C_matrix, group = condition_df$condition)

simp_BL225C_sum <- summary(simp_BL225C)

#save the object simp_BL225C_sum to csv file:
write.csv(simp_BL225C_sum$condition_camporegio_vs_blank_condition_lodi_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_BL225C/simper_BL225C_campor_lodi_ord.csv", 
          row.names = TRUE)

write.csv(simp_BL225C_sum$condition_camporegio_vs_blank_condition_luteolin_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_BL225C/simper_BL225C_campor_luteo_ord.csv", 
          row.names = TRUE)

write.csv(simp_BL225C_sum$condition_camporegio_vs_blank_condition_verbena_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_BL225C/simper_BL225C_campor_verb_ord.csv", 
          row.names = TRUE)

write.csv(simp_BL225C_sum$condition_lodi_vs_blank_condition_luteolin_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_BL225C/simper_BL225C_lodi_luteo_ord.csv", 
          row.names = TRUE)

write.csv(simp_BL225C_sum$condition_lodi_vs_blank_condition_verbena_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_BL225C/simper_BL225C_lodi_verb_ord.csv", 
          row.names = TRUE)

write.csv(simp_BL225C_sum$condition_luteolin_vs_blank_condition_verbena_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_BL225C/simper_BL225C_lueto_verb_ord.csv", 
          row.names = TRUE)



```


```{r}
#strain hybrid
#create the objects for the simper function

library(vegan)
library(reshape2)

setwd("/home/workstation/Scrivania/MARTINA/DEGs Analysis")

strain_hybrid <- read.csv("Hybrid_countdata.csv", sep = ",")

strain_hybrid_matrix <- acast(strain_hybrid, strain_hybrid$id ~ strain_hybrid$sample, value.var = "FoldChange")

strain_hybrid_matrix[is.na(strain_hybrid_matrix)] = 0

condition_df

simp_hybrid <- vegan::simper(strain_hybrid_matrix, group = condition_df$condition)

simp_hybrid_sum <- summary(simp_hybrid)


#save the object simp_hybrid_sum to csv file:
write.csv(simp_hybrid_sum$condition_camporegio_vs_blank_condition_lodi_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_hybrid/simper_hybrid_campor_lodi_ord.csv", 
          row.names = TRUE)

write.csv(simp_hybrid_sum$condition_camporegio_vs_blank_condition_luteolin_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_hybrid/simper_hybrid_campor_luteo_ord.csv", 
          row.names = TRUE)

write.csv(simp_hybrid_sum$condition_camporegio_vs_blank_condition_verbena_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_hybrid/simper_hybrid_campor_verb_ord.csv", 
          row.names = TRUE)

write.csv(simp_hybrid_sum$condition_lodi_vs_blank_condition_luteolin_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_hybrid/simper_hybrid_lodi_luteo_ord.csv", 
          row.names = TRUE)

write.csv(simp_hybrid_sum$condition_lodi_vs_blank_condition_verbena_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_hybrid/simper_hybrid_lodi_verb_ord.csv", 
          row.names = TRUE)

write.csv(simp_hybrid_sum$condition_luteolin_vs_blank_condition_verbena_vs_blank,
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/Strain_hybrid/simper_hybrid_luteo_verb_ord.csv", 
          row.names = TRUE)


```


```{r}
#save the object simp_1021 to csv file (unnecessary):
write.csv(cbind(sample = simp_1021$condition_camporegio_vs_blank_condition_lodi_vs_blank$species, 
                id_gene = counts1021$id,
                average = simp_1021$condition_camporegio_vs_blank_condition_lodi_vs_blank$average,
                overall = simp_1021$condition_camporegio_vs_blank_condition_lodi_vs_blank$overall,
                sd = simp_1021$condition_camporegio_vs_blank_condition_lodi_vs_blank$sd,
                ratio = simp_1021$condition_camporegio_vs_blank_condition_lodi_vs_blank$ratio,
                ava = simp_1021$condition_camporegio_vs_blank_condition_lodi_vs_blank$ava,
                avb = simp_1021$condition_camporegio_vs_blank_condition_lodi_vs_blank$avb,
                ord = simp_1021$condition_camporegio_vs_blank_condition_lodi_vs_blank$ord,
                cusum = simp_1021$condition_camporegio_vs_blank_condition_lodi_vs_blank$cusum,
                p = simp_1021$condition_camporegio_vs_blank_condition_lodi_vs_blank$p), 
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/simper_1021_campor_lodi.csv", 
          row.names = TRUE)

write.csv(cbind(sample = simp_1021$condition_camporegio_vs_blank_condition_luteolin_vs_blank$species, 
                id_gene = counts1021$id,
                average = simp_1021$condition_camporegio_vs_blank_condition_luteolin_vs_blank$average,
                overall = simp_1021$condition_camporegio_vs_blank_condition_luteolin_vs_blank$overall,
                sd = simp_1021$condition_camporegio_vs_blank_condition_luteolin_vs_blank$sd,
                ratio = simp_1021$condition_camporegio_vs_blank_condition_luteolin_vs_blank$ratio,
                ava = simp_1021$condition_camporegio_vs_blank_condition_luteolin_vs_blank$ava,
                avb = simp_1021$condition_camporegio_vs_blank_condition_luteolin_vs_blank$avb,
                ord = simp_1021$condition_camporegio_vs_blank_condition_luteolin_vs_blank$ord,
                cusum = simp_1021$condition_camporegio_vs_blank_condition_luteolin_vs_blank$cusum,
                p = simp_1021$condition_camporegio_vs_blank_condition_luteolin_vs_blank$p), 
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/simper_1021_campor_luteo.csv", 
          row.names = TRUE)

write.csv(cbind(sample = simp_1021$condition_camporegio_vs_blank_condition_verbena_vs_blank$species, 
                id_gene = counts1021$id,
                average = simp_1021$condition_camporegio_vs_blank_condition_verbena_vs_blank$average,
                overall = simp_1021$condition_camporegio_vs_blank_condition_verbena_vs_blank$overall,
                sd = simp_1021$condition_camporegio_vs_blank_condition_verbena_vs_blank$sd,
                ratio = simp_1021$condition_camporegio_vs_blank_condition_verbena_vs_blank$ratio,
                ava = simp_1021$condition_camporegio_vs_blank_condition_verbena_vs_blank$ava,
                avb = simp_1021$condition_camporegio_vs_blank_condition_verbena_vs_blank$avb,
                ord = simp_1021$condition_camporegio_vs_blank_condition_verbena_vs_blank$ord,
                cusum = simp_1021$condition_camporegio_vs_blank_condition_verbena_vs_blank$cusum,
                p = simp_1021$condition_camporegio_vs_blank_condition_verbena_vs_blank$p), 
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/simper_1021_campor_verb.csv", 
          row.names = TRUE)

write.csv(cbind(sample = simp_1021$condition_lodi_vs_blank_condition_luteolin_vs_blank$species, 
                id_gene = counts1021$id,
                average = simp_1021$condition_lodi_vs_blank_condition_luteolin_vs_blank$average,
                overall = simp_1021$condition_lodi_vs_blank_condition_luteolin_vs_blank$overall,
                sd = simp_1021$condition_lodi_vs_blank_condition_luteolin_vs_blank$sd,
                ratio = simp_1021$condition_lodi_vs_blank_condition_luteolin_vs_blank$ratio,
                ava = simp_1021$condition_lodi_vs_blank_condition_luteolin_vs_blank$ava,
                avb = simp_1021$condition_lodi_vs_blank_condition_luteolin_vs_blank$avb,
                ord = simp_1021$condition_lodi_vs_blank_condition_luteolin_vs_blank$ord,
                cusum = simp_1021$condition_lodi_vs_blank_condition_luteolin_vs_blank$cusum,
                p = simp_1021$condition_lodi_vs_blank_condition_luteolin_vs_blank$p), 
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/simper_1021_lodi_luteo.csv", 
          row.names = TRUE)

write.csv(cbind(sample = simp_1021$condition_lodi_vs_blank_condition_verbena_vs_blank$species, 
                id_gene = counts1021$id,
                average = simp_1021$condition_lodi_vs_blank_condition_verbena_vs_blank$average,
                overall = simp_1021$condition_lodi_vs_blank_condition_verbena_vs_blank$overall,
                sd = simp_1021$condition_lodi_vs_blank_condition_verbena_vs_blank$sd,
                ratio = simp_1021$condition_lodi_vs_blank_condition_verbena_vs_blank$ratio,
                ava = simp_1021$condition_lodi_vs_blank_condition_verbena_vs_blank$ava,
                avb = simp_1021$condition_lodi_vs_blank_condition_verbena_vs_blank$avb,
                ord = simp_1021$condition_lodi_vs_blank_condition_luteolin_vs_blank$ord,
                cusum = simp_1021$condition_lodi_vs_blank_condition_verbena_vs_blank$cusum,
                p = simp_1021$condition_lodi_vs_blank_condition_verbena_vs_blank$p), 
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/simper_1021_lodi_verb.csv", 
          row.names = TRUE)

write.csv(cbind(sample = simp_1021$condition_luteolin_vs_blank_condition_verbena_vs_blank$species, 
                id_gene = counts1021$id,
                average = simp_1021$condition_luteolin_vs_blank_condition_verbena_vs_blank$average,
                overall = simp_1021$condition_luteolin_vs_blank_condition_verbena_vs_blank$overall,
                sd = simp_1021$condition_luteolin_vs_blank_condition_verbena_vs_blank$sd,
                ratio = simp_1021$condition_luteolin_vs_blank_condition_verbena_vs_blank$ratio,
                ava = simp_1021$condition_luteolin_vs_blank_condition_verbena_vs_blank$ava,
                avb = simp_1021$condition_luteolin_vs_blank_condition_verbena_vs_blank$avb,
                ord = simp_1021$condition_luteolin_vs_blank_condition_verbena_vs_blank$ord,
                cusum = simp_1021$condition_luteolin_vs_blank_condition_verbena_vs_blank$cusum,
                p = simp_1021$condition_luteolin_vs_blank_condition_verbena_vs_blank$p), 
          file = "/home/workstation/Scrivania/MARTINA/Simper_Analysis/simper_1021_luteo_verb.csv", 
          row.names = TRUE)
```


```{r}
library(vegan)

setwd("/home/workstation/Scrivania/MARTINA/DEGs Analysis")

strain_1021 <- read.csv("Counts1021.csv", sep = ",")

strain_1021 <- data.matrix(strain_1021)

condition <- factor(c("condition_camporegio_vs_blank","condition_lodi_vs_blank","condition_luteolin_vs_blank", "condition_verbena_vs_blank"))

condition_df <- data.frame(condition)

simp_1021 <- with(condition_df, simper(strain_1021, ))
```


```{r}
library(vegan)

#simper test

setwd("C:/Users/Lisa Cangioli/Desktop/PICRUST2/lisa_picrust2_grano/output/pathways_out/files and results")

tab <- read.csv("path_abun_unstrat.csv", sep=";")

tab = subset(tab, select = -c(pathway) )

 

ttab <- read.csv("t_tab.csv", sep=",")

ttab = subset(ttab, select = -c(variety, sample) )

ttab_env <- read.csv("data_env.csv")

ttab <- data.matrix(ttab)

sim <- with(ttab_env, simper(ttab, variety))

simsum <- summary(sim)
```

